Psychological Needs During Intergroup Contact

### 2021-11-04 Methods-and-Results.tex
after re-base

The study itself consisted of three main parts, an introductory
pre-measurement, and the daily experience sampling measurements, as well
as a concluding post-measurement. After giving informed consent,
participants started by filling in an online pre-questionnaire assessing
demographics and general information about their immigration. Over the
next thirty days, the participants then were invited twice a day (at 12
pm and 7pm) to reflect upon their interactions, psychological need
fulfillments, and current attitudes towards the Dutch outgroup
(\textit{median duration} = 22, \textit{MAD duration} = 19). General
compliance was high (85.90\% of all invited surveys were filled
in)\footnote{Two participants completed only two days (among the others, participation was 93.70\%)}.
The response rates were approximately equal during mornings (\textit{n}
= 621) and afternoons (\textit{n} = 604) and most measurements were
completed within four hours of the invitation. After the final day of
daily diary measurements, participants were invited to fill in a longer
post measurement survey that mirrored the pre-measurement. All key
variables in for this study were part of the short daily diary surveys.

@@

The study procedure mirrored the setup of study one and consisted of
pre-, daily diary-, and post-measurement. The participants were invited
for daily diary measurements twice a day (at 12 pm and 7pm) for 30 days
(\textit{median duration} = 46, \textit{MAD duration} = 54). General
compliance was high (70.87\% of all invited surveys were filled in). The
response rates were approximately equal during mornings (\textit{n} =
2608) and afternoons (\textit{n} = 2357). All key variables in for this
study were part of the short daily diary surveys.

@@

The study procedure mirrored the setup of studies one and two, in that
it consisted of pre-, daily diary-, and post-measurement. The
participants were invited for daily diary measurements twice a day (at
12 pm and 7pm) for 30 days (\textit{median duration} = 13,
\textit{MAD duration} = 6). General compliance was high (93.30\% filled
daily diary surveys for 31 days or more NEED TO RE-CHECK THIS). The
response rates were approximately equal during mornings (\textit{n} =
2092) and afternoons (\textit{n} = 2015). All key variables in for this
study were part of the short daily diary surveys.

@@

The measurement of intergroup contacts was identical to study two. The
participants recorded between 1--71 (2.13--87.18\% of individual daily
diary measurements; 41.44\% of all 4107 daily diary responses).

>>>>

The study itself consisted of three main parts, an introductory
pre-measurement, and the daily experience sampling measurements, as well
as a concluding post-measurement. After giving informed consent,
participants started by filling in an online pre-questionnaire assessing
demographics and general information about their immigration. Over the
next thirty days, the participants then were invited twice a day (at 12
pm and 7pm) to reflect upon their interactions, psychological need
fulfillments, and current attitudes towards the Dutch outgroup
(\textit{median duration} = 2M 22S, \textit{MAD duration} = 1M 19S).
General compliance was high (85.90\% of all invited surveys were filled
in)\footnote{Two participants completed only two days (among the others, participation was 93.70\%)}.
The response rates were approximately equal during mornings (\textit{n}
= 621) and afternoons (\textit{n} = 604) and most measurements were
completed within four hours of the invitation. After the final day of
daily diary measurements, participants were invited to fill in a longer
post measurement survey that mirrored the pre-measurement. All key
variables in for this study were part of the short daily diary surveys.

@@

The study procedure mirrored the setup of study one and consisted of
pre-, daily diary-, and post-measurement. The participants were invited
for daily diary measurements twice a day (at 12 pm and 7pm) for 30 days
(\textit{median duration} = 3M 46S, \textit{MAD duration} = 1M 54S).
General compliance was high (70.87\% of all invited surveys were filled
in). The response rates were approximately equal during mornings
(\textit{n} = 2608) and afternoons (\textit{n} = 2357). All key
variables in for this study were part of the short daily diary surveys.

@@

The study procedure mirrored the setup of studies one and two, in that
it consisted of pre-, daily diary-, and post-measurement. The
participants were invited for daily diary measurements twice a day (at
12 pm and 7pm) for 30 days (\textit{median duration} = 4M 13S,
\textit{MAD duration} = 2M 6S). General compliance was high (93.30\%
filled daily diary surveys for 31 days or more NEED TO RE-CHECK THIS).
The response rates were approximately equal during mornings (\textit{n}
= 2092) and afternoons (\textit{n} = 2015). All key variables in for
this study were part of the short daily diary surveys.

@@

The measurement of intergroup contacts was identical to study two. The
participants recorded between 1--71 interactions with Dutch outgroup
members (2.13--87.18\% of individual daily diary measurements; 41.44\%
of all 4107 daily diary responses).

### 2021-11-04 PreregristrationS3/PreregistrationAOT-M.Rmd
after re-base

1. \label{hyp:contact}Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for changes in more favorable outgroup attitudes.
    a. \label{hyp:contactFreq}Participants with more intergroup interactions should have a more favorable outgroup attitudes.
    b. \label{hyp:contactDummy}Outgroup attitudes should be more positive after an intergroup interaction compared to a non-outgroup interaction.
    c. \label{hyp:contactFreqQual}Participants with more intergroup interactions should have a more favorable outgroup attitudes depending on the average interaction quality.
2. \label{hyp:AllportsConditions}Based on Allport's optimal contact conditions, intergroup interactions with equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
    a. \label{hyp:AllportsPred}Based on Allport's optimal contact conditions, outgroup attitudes should be more favorable after intergroup interactions with equal status, common goals, collaboration, and structural support.
    b. \label{hyp:AllportsQuality}Based on past research on the role of interaction quality, interaction quality should be more perceived as more favorable after intergroup interactions with equal status, common goals, collaboration, and structural support.
    c. \label{hyp:AllportsQualityMediation}Based on past research on the role of interaction quality, the variance explained in outgroup attitudes by Allport's optimal contact should to a large extend be assumed by interaction quality.
3. \label{hyp:keyNeed}Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
    a. \label{hyp:keyNeedPred}Outgroup attitudes should be more favorable after intergroup interactions with high key need fulfillment.
    b. \label{hyp:keyNeedQual}Interaction Quality should be perceived as more positive after intergroup interactions with higher key need fulfillment.
    c. \label{hyp:keyNeedMediation}The variance explained in outgroup attitudes by key need fulfillment should to a large extend be explained by interaction quality.
    d. \label{hyp:keyNeedContactType}The effect of key need fulfillment on outgroup attitudes should be specific to intergroup interactions and not be due to need fulfillment in general. Thus, the effect of key need fulfillment on outgroup attitudes should stronger for intergroup interact than for ingroup interactions.
    e. \label{hyp:keyNeedSDT}The effect of key need fulfillment on outgroup attitudes should be persist even when taking other fundamental psychological needs into account. Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for autonomy, competence, and relatedness fulfillment during the interaction (cf., self-determination theory). 
4. \label{hyp:comparison}Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict outgroup attitudes at least as well as Allport's conditions.
    a. \label{hyp:compModel}The need model (H\ref{hyp:keyNeedPred}) should predict more variance in outgroup attitudes than the model based on Allport's conditions (H\ref{hyp:AllportsPred}).
    b. \label{hyp:compTogether}The  effect of key need fulfillment on outgroup attitudes should  persist even when taking other Allport's conditions into account. Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for equal status, common goals, collaboration, and structural support.

@@

1. Entry Survey: A pre-measurement questionnaire (appr. 25 minutes) including demographic information, and relations to the Dutch majority. (payment: 2 Euros)
2. Experience Recaps: At least 30 days of short reflection surveys (appr. 3—5 minutes) on intergroup interactions twice a day. (payment: 1 Euro per Recap; up to 2 Euros per day)
3. Conclusion Survey: On the last day, we conclude with a post-measurement questionnaire (appr. 25 minutes) with some questions on habits and reflections on the study. (payment: 2 Euros)

After the initial 30 day duration, participants are offered the possibility to continue participating in the study either with payment if daily diary measures were missed during the initial study phase or without payment after a total of 60 daily diary measurements were completed. After the initial 30-day period, participants receive automated feedback visualizing the development of their own well-being, attitudes, and motive responses as an additional initiative to give participants access to their own data and to compensate study participation.

@@

The ultimate sampling procedure decision was made as a practical balancing of the number of participants and the number of measurements provided by each participants. Given that this study primarily focuses on the contemporaneous effects within the daily diary measurements, power should thus be high enough.

@@

1. Key Need Fulfillment

@@

# References
## 
\vspace{-2pc}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{-1in}
\setlength{\parskip}{8pt}
\noindent

>>>>

1. \label{hyp:contact}Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for changes in more favorable outgroup attitudes.
    a. \label{hyp:contactFreq}Participants with more intergroup interactions should have more favorable outgroup attitudes.
    b. \label{hyp:contactDummy}Outgroup attitudes should be more positive after an intergroup interaction compared to a non-outgroup interaction.
    c. \label{hyp:contactFreqQual}Participants with more intergroup interactions should have more favorable outgroup attitudes depending on the average interaction quality.
2. \label{hyp:AllportsConditions}Based on Allport's optimal contact conditions, intergroup interactions with equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
    a. \label{hyp:AllportsPred}Based on Allport's optimal contact conditions, outgroup attitudes should be more favorable after intergroup interactions with equal status, common goals, collaboration, and structural support.
    b. \label{hyp:AllportsQuality}Based on past research on the role of interaction quality, interaction quality should be perceived as more positive after intergroup interactions with equal status, common goals, collaboration, and structural support.
    c. \label{hyp:AllportsQualityMediation}Taken together, the variance explained in outgroup attitudes by Allport's optimal contact should to a large extend be explained by interaction quality.
3. \label{hyp:keyNeed}Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
    a. \label{hyp:keyNeedPred}Outgroup attitudes should be more favorable after intergroup interactions with high key need fulfillment.
    b. \label{hyp:keyNeedQual}Interaction Quality should be perceived as more positive after intergroup interactions with higher key need fulfillment.
    c. \label{hyp:keyNeedMediation}The variance explained in outgroup attitudes by key need fulfillment should to a large extend be explained by interaction quality.
    d. \label{hyp:keyNeedContactType}The effect of key need fulfillment on outgroup attitudes should be specific to intergroup interactions and not be due to need fulfillment in general. Thus, the effect of key need fulfillment on outgroup attitudes should be stronger for intergroup interact than for non-outgroup interactions (or need fulfillment during a time of no interaction).
    e. \label{hyp:keyNeedSDT}The effect of key need fulfillment on outgroup attitudes should persist even when taking other fundamental psychological needs into account. Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for autonomy, competence, and relatedness fulfillment during the interaction (cf., self-determination theory). 
4. \label{hyp:comparison}Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict outgroup attitudes at least as well as Allport's conditions.
    a. \label{hyp:compModel}The need model (H\ref{hyp:keyNeedPred}) should predict more variance in outgroup attitudes than the model based on Allport's conditions (H\ref{hyp:AllportsPred}).
    b. \label{hyp:compTogether}The  effect of key need fulfillment on outgroup attitudes should  persist even when taking Allport's conditions into account. Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for equal status, common goals, collaboration, and structural support.

@@

1. Entry Survey: A pre-measurement questionnaire (appr. 25 minutes) including demographic information, and relations to the Dutch majority (payment: 2 Euros).
2. Experience Recaps: At least 30 days of short reflection surveys (appr. 3—5 minutes) on intergroup interactions twice a day (payment: 1 Euro per Recap; up to 2 Euros per day).
3. Conclusion Survey: On the last day, we conclude with a post-measurement questionnaire (appr. 25 minutes) with some questions on habits and reflections on the study (payment: 2 Euros).

After the initial 30 day duration, participants are offered the possibility to continue participating in the study either with payment if daily diary measures were missed during the initial study phase or without payment after a total of 60 daily diary measurements were completed. After the initial 30-day period, participants receive automated feedback visualizing the development of their own well-being, attitudes, and motive responses as an additional initiative and to give participants access to their own data and to compensate study participation.

@@

The ultimate sampling procedure decision was made as a practical balancing of the number of participants and the number of measurements provided by each participants. Given that this study primarily focuses on the contemporaneous effects within the daily diary measurements, power should be high enough.

@@

1. Key Need fulfillment

@@

## 
\vspace{-2pc}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{-1in}
\setlength{\parskip}{8pt}
\noindent
